---
output:
  html_document:
    includes:
      in_header: hero-image.html
      after_body: footer.html
---

<style type="text/css">
.main-container {
    max-width: 1170px;
    
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This website presents a typological database of the extended functions of 'truth'-words.


---

### Questionnaire

The database was collected using the following questionnaire.

```{r, echo=FALSE}
library(knitr)
column_description <- tibble::tribble(
  ~tag, ~description, ~stimulus,
   "`truth_pred`", "", "It’s the truth. [It is not made up, it is how things are]",
  "`truth_n`",  "", "He always tells the truth.",
  "`truth_adj`",  "", "It is a true story [I’m not lying]",
  "`right`",  "", "Is this the right answer? [Or is it the wrong answer?]",
  "`genuine`",  "", "Are these documents real? [Or are they fakes?]",
  "`real`",  "", "She thinks Narnia is a real country. [It’s actually made up]",
  "`CL`",  "", "He is a true fighter [He has all the qualities characteristic of a fighter]",
  "`int_adj`",  "", "She is a very beautiful woman",
  "`int_adv`",  "", "I’m very happy that he came",
  "`really_pred`",  "", "I am really writing a book [even though they said I couldn’t]",
  "`int_pred`",  "", "I really want to go [I can’t stand it here]",
  "`select`",  "", "The real problem is that we don’t have water [that’s what we have to focus on]",
  "`tag`",  "", "The weather is great today, right? ",
  "`affirm`",  "", "[The weather is great today, right?] Yes, it is.",
  "`conc_pred1`",  "", "He is a good person, although/admittedly (but the truth is) he brags a lot.",
  "`conc_pred2`",  "", "Although he is young, he is a skilled doctor. (He is indeed young, but he is a skilled doctor)",
  "`conc_adj`",  "", "We were at a good, although expensive, restaurant yesterday.",
  "`conc_adv`",  "", "The buses run, although rarely.",
  "`subj`",  "", "Frankly speaking (to tell the truth), I don’t like this idea."
  )
kable(column_description)
```

---

### Languages

The sample includes 50 languages spoken in Eurasia.
```{r, include=FALSE, echo=FALSE}
library(tidyverse)
library(lingtypology)
df <- read.csv("data.csv", na.strings=c("","NA"))
```

```{r, echo=FALSE, out.width = '100%'}
df%>%
  select("language_name", "family") -> lngs
lngs <-unique(lngs)
  
map.feature(languages = lngs$language_name,
            features = lngs$family,
            label = lngs$language,
            tile = "Esri.WorldPhysical",
            color = "darkgreen",
            width = 6
            )
```

'Truth'-words analyzed in each of the languages are listed in the table below.

```{r echo = FALSE, results = 'asis', message=FALSE, warning=FALSE}
library(tidyverse)
library(readr)
library(DT)

df <- read.csv("data.csv", na.strings=c("","NA"))
df %>%
  filter(df$truth_word == "yes") %>%
  select("language_name", "iso", "family", "consultant", "word", "translation") -> df

df <- unique(df)


datatable(
  data = df,
  filter = "top")

```




---

### How to cite

If you use this database in your research, please cite as follows:

```{}
Bandarenko, Alice, Anastasia Panova & Anna Sjöberg. 2024. Extended functions of 'truth'-words. A typological database. Stockholm: Stockholm University.
```



---